---
title: "hueniverrrsity-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hueniverrrsity-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hueniverrrsity)
```

# Introduction

All universities or colleges have a visual identity defined by specific colours and fonts. This enables all publications from a given university to have a cohesive theme and be immediatley identifiable. 

[hueniverrrsity](https://github.com/UBC-MDS/hueniversitypy) is a package designed to apply the visual themes of four Canadian Universities to ggplot2 objects, McGill University, University of Toronto, University of Alberta and the University of British Columbia. 

## hueniverrrsity Functions

* `theme_alberta()` - Applies the U of A visual identity to ggplot2 objects.
  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()`
  - `colour_palette`: `alpha`, `beta`, `gamma` or `delta`
    colour palettes are different colour combinations specified in the U of A visual identity

* `theme_mcgill()` - Applies the McGill visual identity to ggplot2 objects.

  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()`

* `theme_toronto()` - Applies the U of T visual identity to ggplot2 objects.

  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()`
  - `colour_palette`: `vibrant`, `cool` or `awards`
    colour palettes are different colour combinations specified in the U of T visual identity

* `theme_ubc()` - Applies the UBC visual identity to ggplot2 objects.
  
  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()`
        
## Examples

- `theme_alberta()`

``` r
# Create scatter plot
a1 <- ggplot(data=mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
  geom_point(size = 3, alpha = 0.8) +
  theme_alberta('colour', 'beta')

# Create density plot
a2 <- ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha = 0.8) +
  theme_alberta('fill', 'delta')

ggarrange(a1, a2, ncol=2, common.legend = TRUE)
```

- `theme_mcgill()`

``` r
# Create scatter plot
m1 <- ggplot(data = mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
  geom_point(size = 3, alpha = 0.8) +
  theme_mcgill('colour')

# Create density plot
m2 <- ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha=0.8) +
  theme_mcgill('fill')

ggarrange(m1, m2, ncol=2, common.legend = TRUE)
```

- `theme_toronto()`

``` r
# Create scatter plot
t1 <- ggplot(data = mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
  geom_point(size = 2.5) +
  theme_toronto('colour', 'vibrant')

# Create density plot
t2 <- ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha = 0.8) +
  theme_toronto('fill', 'awards')

ggarrange(t1, t2, ncol=2, common.legend = TRUE)
```

- `theme_ubc()`

``` r
# Create scatter plot
u1 <- ggplot(data = mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
geom_point(size = 2.5) +
theme_ubc('colour')

# Create density plot
u2 <- ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
geom_density(alpha=0.8) +
theme_ubc('fill')

ggarrange(u1, u2, ncol=2, common.legend = TRUE)
```

