---
title: "hueniverrrsity-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hueniverrrsity-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hueniverrrsity)
library(ggplot2)
```

# Introduction

All universities and colleges have a visual identity composed of their specific colours and typefaces. This enables all publications from a given university to have a cohesive theme and be immediately identifiable. 

[hueniverrrsity](https://github.com/UBC-MDS/hueniversitypy) is a package designed to apply the visual themes of four Canadian Universities to ggplot2 objects. The package currently supports the visual identities of University of Alberta, McGill University, the University of Toronto, and the University of British Columbia. 

## Functions

* `theme_alberta()` - Applies the U of A visual identity to ggplot2 objects.
  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()`
  - `colour_palette`: `alpha`, `beta`, `gamma` or `delta`
    colour palettes are different colour combinations specified in the U of A visual identity </br>
    
* `theme_mcgill()` - Applies the McGill visual identity to ggplot2 objects.

  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()` </br>

* `theme_toronto()` - Applies the U of T visual identity to ggplot2 objects.

  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()`
  - `colour_palette`: `vibrant`, `cool` or `awards`
    colour palettes are different colour combinations specified in the U of T visual identity </br>

* `theme_ubc()` - Applies the UBC visual identity to ggplot2 objects.
  
  Input:

  - `colour_use`: `fill` or `colour`
      - `colour_use = colour` for `geom_point()` and `geom_line()`
      - `colour_use = fill` for `geom_boxplot()`, `geom_bar()`,
        `geom_violin()` and `geom_histogram()` </br>
        
## Examples

- `theme_alberta()`

``` {r, include = TRUE}
# Create scatter plot
ggplot(data=mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
  geom_point(size = 3, alpha = 0.8) +
  theme_alberta('colour', 'beta')

# Create density plot
ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha = 0.8) +
  theme_alberta('fill', 'delta')
```

- `theme_mcgill()`

``` {r, include = TRUE}
# Create scatter plot
ggplot(data = mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
  geom_point(size = 3, alpha = 0.8) +
  theme_mcgill('colour')

# Create density plot
ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha=0.8) +
  theme_mcgill('fill')
```

- `theme_toronto()`

``` {r, include = TRUE}
# Create scatter plot
ggplot(data = mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
  geom_point(size = 2.5) +
  theme_toronto('colour', 'vibrant')

# Create density plot
ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha = 0.8) +
  theme_toronto('fill', 'awards')
```

- `theme_ubc()`

``` {r, include = TRUE}
# Create scatter plot
ggplot(data = mtcars, aes(x = hp, y = mpg, colour = as.factor(cyl))) +
  geom_point(size = 2.5) +
  theme_ubc('colour')

# Create density plot
ggplot(data = mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha=0.8) +
  theme_ubc('fill')
```

